
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\input{preambule.tex}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Breno Martins da Costa Corrêa e Souza}} & 
    \href{mailto:breno.ec@gmail.com}{breno.ec@gmail.com} \\
  \href{https://www.linkedin.com/in/brenomccs}{LinkedIn \texttt{@brenomccs}} ·
  \href{https://github.com/cognocoder}{GitHub \texttt{@cognocoder}} &
    +55 31 99922 7282 \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CEFET-MG -- Campus II}{Belo Horizonte, Minas Gerais}
      {Master's student in computational mathematical modeling}{Feb. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Development}{Interactive real-time simulation tools written
          in C++ and OpenGL, built through Make, CMake, tested with GoogleTest,
          documented using Doxygen, versioned with Git.}
        \resumeItem{Dissertation}{Text typesetted in \LaTeX and Tikz, built
          using Make.}
      \resumeItemListEnd
    \resumeSubheading
      {CEFET-MG -- Campus II}{Belo Horizonte, Minas Gerais}
      {Bachelor's degree in Computer Engineering}{Aug. 2009 -- Mar. 2015}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CEFET-MG -- Campus V}{Divinópolis, Minas Gerais}
      {Substitute Teacher}{2018 -- 2019}
      \resumeItemListStart
        \resumeItem{Teaching}{Computer Programming in C/C++ and Java,
          Relational Databases in SQL.}
        \resumeItem{Orientation}{Technical software, report and card game
          production.}
        \resumeItem{Organization \& arbitration}{Regional and state stages of the
          Brazilian Robotics Olympiad.}
      \resumeItemListEnd

    \resumeSubheading
      {Mav Tecnologia}{Belo Horizonte, Minas Gerais}
      {System Analyst}{2014}
      \resumeItemListStart
        \resumeItem{Web Development}{Project prototyping and planning for
          company fusion with the Internet in Java, GWT, HTML, CSS and Python.}
      \resumeItemListEnd

    \resumeSubheading
      {Take Blip}{Belo Horizonte, Minas Gerais}
      {Research \& Development Intern}{2012 -- 2014}
      \resumeItemListStart
        \resumeItem{Full Stack Development}{Messaging and promotional platforms
          with SMS and Web interfaces using C\#, {.NET} Web API, {.NET} MVC,
          Entity Framework and SQL Server. Reduced event table entries by three
          orders of magnitude by removing unnecessary records and simplifying
          maintenance queries, which result in better overall performance and
          storage usage.}
      \resumeItemListEnd

    \resumeSubheading
      {DCSA/CEFET-MG -- Campus II}{Belo Horizonte, Minas Gerais}
      {Information Technology Intern}{2010 -- 2012}
      \resumeItemListStart
        \resumeItem{Web Development}{Web portal maintenance and other
          technological affairs using Java Server Pages, JavaScript, HTML, CSS
          and OpenCMS.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://cognocoder.github.io/coniventes/}{Coniventes}}
      {Personal project aimed to empower society with a mobile first GitHub Page
      written in JavaScript, HTML and {CSS}.
      It features public data crawled using Node.js, fuzzy search and on demand
      picture loading, in order to save user mobile data.
      Google Analytics registered almost 2000 unique viewers and close to 4000
      visualizations.}
  \resumeSubHeadingListEnd

\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CILAMCE 2017}{Florianópolis, Santa Catarina}
      {Speaker recognition with artificial neural networks}{2017}
  \resumeSubHeadingListEnd

\section{Programming Skills \& Technologies}
  \resumeSubHeadingListStart
    \resumeSubItem{Intermediate skill level}{%
      Well versed in Web development using \textbf{HTML}, \textbf{CSS} and
      \textbf{JavaScript}.
      \textbf{C/C++} with \textbf{CMake}, \textbf{Doxygen}, \textbf{Make} and
      \textbf{GoogleTest}, using \textbf{agile methodologies} and \textbf{Git}
      for version control.}
    \resumeSubItem{Beginner skill level}{.NET, C\#, Java, MongoDB, Node.js,
      OpenGL, Python, PyTest, React and SQL.}
  \resumeSubHeadingListEnd

\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{Native}{Portuguese}
    \resumeSubItem{Fluent}{English}
    \resumeSubItem{Beginner}{French}
  \resumeSubHeadingListEnd

\end{document}
